---
title: "Plant_1_Linreg_Daily"
author: "tanchuanxin"
date: "11/1/2021"
output: html_document
---

<h1>Setup</h1>
We will perform the necessary imports, and change the working directory based on the user 

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(rpart)
library(rpart.plot)
library(car)
library(corrplot)
library(tidyverse)
library(caTools)
library(ggplot2)
library(lubridate)
library(TTR)
library(tsbox)




# setwd("C:/Users/matth/Desktop/Course Materials for Stu/AY21 Team Assignment and Project") 
setwd("C:/Users/user/Documents/Github/project-MAI") # chuanxin's wd
set.seed(2021)
seed = 2021
# load dataset
plant_1.dt <- fread("Plant_1_Data.csv")

# convert some features into factors where relevant
plant_1.dt$SOURCE_KEY <- factor(plant_1.dt$SOURCE_KEY)
plant_1.dt$DOTW <- factor(plant_1.dt$DOTW)
plant_1.dt$TIME <- factor(plant_1.dt$TIME)
plant_1.dt$DATE <- factor(plant_1.dt$DATE)

head(plant_1.dt)

```


<h1>Load in the data</h1>
Perform some cleaning on the data 

```{r cleaning}
# remove some of the extra features that we have
linreg_daily_yield.dt <- subset(plant_1.dt, select = -c(TIME, PLANT_ID, DOTW, DATE_TIME, PERIOD_YIELD, TOTAL_YIELD, DC_POWER, AC_POWER))

head(linreg_daily_yield.dt)

# get the mean values across most columns
linreg_daily_yield.dt1 <- linreg_daily_yield.dt %>%
  group_by(SOURCE_KEY, DATE) %>%
    summarise(across(AMBIENT_TEMPERATURE:`Rainfall (kg/m2)`, mean))

# get the max values of daily yield (this is the true daily yield)
linreg_daily_yield.dt2 <- linreg_daily_yield.dt %>%
  group_by(SOURCE_KEY, DATE) %>%
    summarise(across(DAILY_YIELD, max))

# concat and remove date
linreg_daily_yield.dt <- merge(linreg_daily_yield.dt1, linreg_daily_yield.dt2, by=c("SOURCE_KEY", "DATE"), all = T)

linreg_daily_yield.dt <- subset(linreg_daily_yield.dt, select = -c(DATE))

# check if correct
dim(linreg_daily_yield.dt1)
head(linreg_daily_yield.dt1)
dim(linreg_daily_yield.dt2)
head(linreg_daily_yield.dt2)
dim(linreg_daily_yield.dt)
head(linreg_daily_yield.dt)
```

<h1>Removing correlated variables</h1>

``` {r lin_reg_model_all}
M = cor(subset(linreg_daily_yield.dt, select = -c(DAILY_YIELD, SOURCE_KEY)))
corrplot(M, method = "number")
# We discover that MODULE_TEMPERATURE is very highly correlated with both AMBIENT_TEMPERATURE and IRRADIATION, while `Relative Humidity (%)` and `Rainfall (kg/m2)` are also highly correlated


m1 <- lm(DAILY_YIELD ~ .-SOURCE_KEY, data = linreg_daily_yield.dt)
summary(m1)
vif(m1)
# we see that MODULE_TEMPERATURE has the highest VIF value of 27.6 > 10, we try and exclude that first

m2 <- lm(DAILY_YIELD ~ .-SOURCE_KEY -MODULE_TEMPERATURE, data = linreg_daily_yield.dt)
summary(m2)
vif(m2)
# now all the VIF values are <10



# With selected features, develop model on trainset
train <- sample.split(Y = linreg_daily_yield.dt$DAILY_YIELD, SplitRatio = 0.7)
trainset <- subset(linreg_daily_yield.dt, train == T)
testset <- subset(linreg_daily_yield.dt, train == F)

# Checking the distribution of Y is similar in trainset vs testset.
summary(trainset$DAILY_YIELD)
summary(testset$DAILY_YIELD)
# yes, similar enough

# create model
m3 <- lm(DAILY_YIELD ~ .-SOURCE_KEY -MODULE_TEMPERATURE, data = trainset)
summary(m3)
# residuals(m3)

# we see that AMBIENT_TEMPERATURE, `Relative Humidity (%)` and `Pressure (hPa)` are not statistically significant , we will create another model without these variables 

m4 <- lm(DAILY_YIELD ~ .-SOURCE_KEY -MODULE_TEMPERATURE -AMBIENT_TEMPERATURE -`Relative Humidity (%)` -`Pressure (hPa)`, data = trainset)
summary(m4)
# residuals(m4)

# Residuals = Error = Actual - Model Predicted
RMSE.m4.train <- sqrt(mean(residuals(m4)^2))  # RMSE on trainset based on m4 model.
summary(abs(residuals(m4)))  # Check Min Abs Error and Max Abs Error.

# Apply model from trainset to predict on testset.
predict.m4.test <- predict(m4, newdata = testset)
testset.error <- testset$DAILY_YIELD - predict.m4.test

# Testset Errors
RMSE.m4.test <- sqrt(mean(testset.error^2))
summary(abs(testset.error))

# mean testset error is 365.75      
```

<h1>Check by individual SOURCE_KEY</h1>
The full datasets consists of many panels, and when different data are brought together, it might display some characteristics that were otherwise not present. We will look at each of the panels individually to see if we find anything interesting

``` {r lin_reg_model_by_source_key}
for (level in levels(linreg_daily_yield.dt$SOURCE_KEY)) {
  source_key_DAILY_YIELD.dt <- filter(linreg_daily_yield.dt, SOURCE_KEY==level) %>%
    subset(, -c(SOURCE_KEY))

  m5 <- lm(DAILY_YIELD ~ . -MODULE_TEMPERATURE, data = source_key_DAILY_YIELD.dt)
  paste("levels: ", as.character(level))
  print(summary(m5))
  print(vif(m5))
}


```

<h1>Removing features</h1> 
We see that when considering individual inverters, what stands out is that only one variable is consistently highly significant: IRRADIATION... the rest other variables can be considered for removal

We will remove rainfall first, which shows the least statistically significant result

From before, we know that we should already exclude MODULE_TEMPERATURE, AMBIENT_TEMPERATURE, `Relative Humidity (%)` and `Pressure (hPa)` from the model

``` {r remove_rainfall}
# find a smaller subset of data - we can remove rainfall, since it is the least significant out of all the variables 
linreg_DAILY_YIELD_selected.dt <- subset(linreg_daily_yield.dt, select = -c(MODULE_TEMPERATURE, AMBIENT_TEMPERATURE, `Relative Humidity (%)`, `Pressure (hPa)`, `Rainfall (kg/m2)`))

# With selected features, develop model on trainset
train <- sample.split(Y = linreg_DAILY_YIELD_selected.dt$DAILY_YIELD, SplitRatio = 0.7)
trainset <- subset(linreg_DAILY_YIELD_selected.dt, train == T)
testset <- subset(linreg_DAILY_YIELD_selected.dt, train == F)

# Checking the distribution of Y is similar in trainset vs testset.
summary(trainset$DAILY_YIELD)
summary(testset$DAILY_YIELD)
# yes, similar enough 

# create model
m6 <- lm(DAILY_YIELD ~ .-SOURCE_KEY, data = trainset)
summary(m6)
# residuals(m6)

# Residuals = Error = Actual - Model Predicted
RMSE.m6.train <- sqrt(mean(residuals(m6)^2))  # RMSE on trainset based on m6 model.
summary(abs(residuals(m6)))  # Check Min Abs Error and Max Abs Error.

# Apply model from trainset to predict on testset.
predict.m6.test <- predict(m6, newdata = testset)
testset.error <- testset$DAILY_YIELD - predict.m6.test

# Testset Errors
RMSE.m6.test <- sqrt(mean(testset.error^2))
summary(abs(testset.error))

# mean testset error is 326.852  -- an improvement from 365.75 

```

After removing rainfall, we will try to remove wind direction can

``` {r remove_wind_direction}
# find a smaller subset of data - we can remove wind_direction, since it is the least significant out of all the variables 
linreg_DAILY_YIELD_selected.dt <- subset(linreg_daily_yield.dt, select = -c(MODULE_TEMPERATURE, AMBIENT_TEMPERATURE, `Relative Humidity (%)`, `Pressure (hPa)`, `Rainfall (kg/m2)`, `Wind direction`))

# With selected features, develop model on trainset
train <- sample.split(Y = linreg_DAILY_YIELD_selected.dt$DAILY_YIELD, SplitRatio = 0.7)
trainset <- subset(linreg_DAILY_YIELD_selected.dt, train == T)
testset <- subset(linreg_DAILY_YIELD_selected.dt, train == F)

# Checking the distribution of Y is similar in trainset vs testset.
summary(trainset$DAILY_YIELD)
summary(testset$DAILY_YIELD)
# yes, similar enough 

# create model
m7 <- lm(DAILY_YIELD ~ .-SOURCE_KEY, data = trainset)
summary(m7)
# residuals(m7)

# Residuals = Error = Actual - Model Predicted
RMSE.m7.train <- sqrt(mean(residuals(m7)^2))  # RMSE on trainset based on m7 model.
summary(abs(residuals(m7)))  # Check Min Abs Error and Max Abs Error.

# Apply model from trainset to predict on testset.
predict.m7.test <- predict(m7, newdata = testset)
testset.error <- testset$DAILY_YIELD - predict.m7.test

# Testset Errors
RMSE.m7.test <- sqrt(mean(testset.error^2))
summary(abs(testset.error))

# mean testset error is 375.354 -- worse than 326.852  

```

The other features are now all extremely statistically important, so we will not remove any more features. We are left with only IRRADIATION and `Wind speed (m/s)`



<h1>Dummy variables</h1>
We will investigate if certain dummy variables will be useful in helping us predict the generative capacity of the solar panels. We will build off of the reduced feature set while introducing some features that were removed.

What we have are the following factors that we will use dummy variables for 
1. SOURCE_KEY
    This will indicate if one solar panel is better or worse than the baseline 

``` {r linreg_dummy_var}
linreg_DAILY_YIELD_enhanced.dt <- linreg_DAILY_YIELD_selected.dt

# according to alphabetical order, so we already have time-ordered from earliest to latest
# does not matter which source is the baseline
levels(linreg_DAILY_YIELD_enhanced.dt$SOURCE_KEY)

m8 <- lm(DAILY_YIELD ~ ., data = linreg_DAILY_YIELD_enhanced.dt)
summary(m8)


```


